---
output: github_document
--- 

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# xkcd

<!-- badges: start -->
<!-- badges: end -->

The `xkcd` package provides an R interface to retrieve data about [xkcd comics] (https://xkcd.com) from the xkcd website and view them in your plot window

## Installation

You can install the development version of xkcd from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Anelra/Intro-R-Package")
```

## Browsing Comics

Given a comic number the xckd function retrieves a json object with meta data about that comic.

```{r example}
library(xkcd)

first_comic <- xkcd(1)
first_comic
```

The most useful thing you can do with these objects is plot them, which displays the comic image in your viewer window
```{r cars}
plot(first_comic)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
